Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis in an Idealized, Axisymmetric Framework

### 2018-03-26 paper.tex
Small change to abstract (move definition of theta to earlier in the paragraph.

\abstract{Large changes in tropopause-layer static stability are observed during the rapid intensification (RI) of an idealized, axisymmetric tropical cyclone (TC).
Over the eye, static stability near the tropopause decreases and the cold-point tropopause height rises by up to 4 km at the storm center.
Outside of the eye, static stability increases considerably just above the cold-point tropopause, and the tropopause remains near its initial level.\\
\indent A budget analysis reveals that the advection term, which includes differential advection of potential temperature and direct advection of static stability, is important throughout the upper troposphere and lower stratosphere.
Within the eye, differential advection plays a particularly important role in destabilizing the layer near and above the cold-point tropopause.
Outside of the eye, the upper-tropospheric outflow layer exports high potential temperature ($\theta$) air from the eyewall to large radii in the upper troposphere.
This increase in $\theta$ forces stabilization below the outfow jet and destabilization above.
Vertical wind shear above and below the outflow maximum induces vertical gradients of turbulence, which also modify the vertical stability profile.
Meanwhile, radiative heating tendencies at the top of the cirrus canopy generally act to destabilize the upper troposphere and stabilize the lower stratosphere.
These turbulent and radiative processes combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.}
%The results suggest that turbulence and radiation, alongside advection, play fundamental roles in the upper-level static stability evolution of TCs.}
%The conclusions are robust to changes in the initial thermodynamic profile and prescribed vertical mixing length within a reasonable range of values.}

>>>>

\abstract{Large changes in tropopause-layer static stability are observed during the rapid intensification (RI) of an idealized, axisymmetric tropical cyclone (TC).
Over the eye, static stability near the tropopause decreases and the cold-point tropopause height rises by up to 4 km at the storm center.
Outside of the eye, static stability increases considerably just above the cold-point tropopause, and the tropopause remains near its initial level.\\
\indent A budget analysis reveals that the advection term, which includes differential advection of potential temperature ($\theta$) and direct advection of static stability, is important throughout the upper troposphere and lower stratosphere.
Within the eye, differential advection plays a particularly important role in destabilizing the layer near and above the cold-point tropopause.
Outside of the eye, the upper-tropospheric outflow layer exports high-$\theta$ air from the eyewall to large radii in the upper troposphere.
This increase in $\theta$ forces stabilization below the outfow jet and destabilization above.
Vertical wind shear above and below the outflow maximum induces vertical gradients of turbulence, which also modify the vertical stability profile.
Meanwhile, radiative heating tendencies at the top of the cirrus canopy generally act to destabilize the upper troposphere and stabilize the lower stratosphere.
These turbulent and radiative processes combine to play an important role in the development of the strong stable layer immediately above the cold-point tropopause during RI.}
%The results suggest that turbulence and radiation, alongside advection, play fundamental roles in the upper-level static stability evolution of TCs.}
%The conclusions are robust to changes in the initial thermodynamic profile and prescribed vertical mixing length within a reasonable range of values.}
